\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-02 coq-example.tex
Update number for Analysis Example.

Thus, to implement this generic abstract interpreter, we need to postulate the abstract value and their mathematical property. Then we need to prove the abstract interpreter is \textbf{sound and terminating}  with the help of these postulations. In our implementation, this postulation happens in "absStateData" where we indicate the "lift" of concrete interpretation and the mathematical properties these lifted should satisfy. Then for concrete analyzer, we only need to instantiate these postulation. The construction and proof of soundness uses "FInduction" and "FRecursion", mainly on "exp" and "stmt". 
It takes about 300+ LOCs. 
% This example shows how
% to use family inheritance to extend a concrete interpreter with abstract
% interpreters. 
% This example also shows in this family polymoprhism framework we can reason about "Lang" with computation details being abstracted.

@@

The third family and the fourth family "LangTyping" and "LangCP" instantiate the postulates of the
"LangwAbs" and recover computational information of "analyze". The corresponding fields in "absStateData" is overridden by concrete implementations. The resulting abstract interpreter is expected
to act as a type-analyzer and constant-propagator respectively. It takes about 200+ LOCs. 
% These are two examples of instantiate the detail computation of abstract interpretation.

>>>>

Thus, to implement this generic abstract interpreter, we need to postulate the abstract value and their mathematical property. Then we need to prove the abstract interpreter is \textbf{sound and terminating}  with the help of these postulations. In our implementation, this postulation happens in "absStateData" where we indicate the "lift" of concrete interpretation and the mathematical properties these lifted should satisfy. For example, "absState" is the lift of concrete state, "join" is doing lattice join on two abstract value... Then for concrete analyzer, we only need to instantiate these postulation. The construction and proof of soundness uses "FInduction" and "FRecursion", mainly on "exp" and "stmt". 
It takes about 450 LOCs. 
% This example shows how
% to use family inheritance to extend a concrete interpreter with abstract
% interpreters. 
% This example also shows in this family polymoprhism framework we can reason about "Lang" with computation details being abstracted.

@@

The third family and the fourth family "LangTyping" and "LangCP" instantiate the postulates of the
"LangwAbs" and thus recover computational information of "analyze". "LangCP" also extend "exp" with integer expression. The corresponding fields in "absStateData" is overridden by concrete implementations. The resulting abstract interpreter is expected to act as a type-analyzer and constant-propagator respectively. They takes 200 and 300 LOCs respectively. 
% These are two examples of instantiate the detail computation of abstract interpretation.
